---
title: "Websites"
format: qmdrslides-revealjs
---

## Anatomy of a Project

Websites, like any project, are defined by `_quarto.yml`. 

```yaml
project:
  type: website

website:
  title: "posit-conf"
  navbar:
    left:
      - href: index.qmd
        text: Home
      - about.qmd
```

## Our Turn {.our-turn}

Let's create our first website!

1. Click into `empty-project`
2. Run `quarto create-project --type website`
3. Run `quarto render`
4. Run `quarto publish`

## Your Turn {.your-turn}

Open `websites` and click through the file directories to see what's inside. Try rendering all five of the new .qmd files.

- `syllabus.qmd`
- `intro-to-data/notes.qmd`
- `intro-to-data/ps.qmd`
- `learning-r/notes.qmd`
- `learning-r/ps.qmd`

{{< fa brands discord >}} Post to Discord one piece of Quarto syntax or YAML option that you have never seen before.

```{r}
#| echo: false
countdown::countdown(4)
```


## Our Turn {.our-turn}

Let's add some life to our website.

1. Modify the homepage content a bit
1. Add links to the two `intro-data` notes.
1. Turn on freeze to save computational artifacts.


## Your Turn {.your-turn}

Add more features to the website by:

1. Add two notes from `learning-r` to the sidebar navigation.
1. Modify the [about page](https://quarto.org/docs/websites/website-about.html) to describe a course you would like to teach.
1. Add a link to `syllabus.qmd` in the [top navbar](https://quarto.org/docs/websites/website-navigation.html#top-navigation).
1. [Add an image](https://quarto.org/docs/authoring/figures.html) to the homepage that illustrates "statistics" to you. (note: it's easiest to use a url to an image online)
1. [Add a footer](https://quarto.org/docs/websites/website-navigation.html#page-footer) with and [icon]().
1. Create a toggle between [light and dark mode](https://quarto.org/docs/output-formats/html-themes.html#dark-mode).

```{r}
countdown::countdown(25)
```

## Listings

If you have a class of documents that you will author many of (over time), you can create adaptive navigation using a **Document Listing**.

```yaml
---
title: "Listing Example"
listing:
  contents:
    - "reports/*.qmd"
    - "lab-notes/*reports.qmd"
---
```

## Our Turn {.our-turn}

Let's add a dedicated page for the problem sets.

1. Make a new `ps-home.qmd`.
2. Link to PS in the navbar.
3. Add a [listing](https://quarto.org/docs/websites/website-listings.html) to `ps-home.qmd`.


## Your Turn {.your-turn}

Add a dedicated page for slides.

1. Make a new `slides-home.qmd`.
2. Link to Slides in navbar.
3. Add a [listing](https://quarto.org/docs/websites/website-listings.html) to `ps-home.qmd`.
   1. Change the [listing type](https://quarto.org/docs/websites/website-listings.html#listing-types) to a grid.

```{r}
countdown::countdown(10)
```


## Our Turn {.our-turn}

1. Let's combine the two listings pages
   1. Rename `ps-home.qmd` to `materials.qmd`
   1. Rename `PS` to `Materials` in navbar.
   1. [Combine the listings](https://quarto.org/docs/websites/website-listings.html#multiple-listings).
1. Let's made a dedicated staff website.
   1. Change home page.
   2. Add instructors page and link to it.
   3. Add learning objectives to the notes.
   
## Let's take a break
