---
title: "Websites"
format: qmdrslides-revealjs
---

## Anatomy of a Project

Websites, like any project, are defined by `_quarto.yml`. 

```yaml
project:
  type: website

website:
  title: "posit-conf"
  navbar:
    left:
      - href: index.qmd
        text: Home
      - about.qmd
```

## Our Turn {.our-turn}

Let's create our first website!

1. Click into `empty-project`
2. Run `quarto create-project --type website`
3. Run `quarto render`
4. Run `quarto publish`

## Your Turn {.your-turn}

Open `websites` and click through the file directories to see what's inside. Try rendering all five of the new .qmd files.

- `syllabus.qmd`
- `intro-to-data/notes.qmd`
- `intro-to-data/ps.qmd`
- `learning-r/notes.qmd`
- `learning-r/ps.qmd`

{{< fa brands discord >}} Post to Discord one piece of Quarto syntax or YAML option that you have never seen before.

```{r}
#| echo: false
countdown::countdown(4)
```


## Our Turn {.our-turn}

Let's add some life to our website.

1. Modify the homepage a bit.
2. Add a theme


## Your Turn {.your-turn}

Add more features to the website by:

1. Add an image to the homepage.
2. Add a footer
3. Create a toggle between light and dark mode

```{r}
countdown::countdown(20)
```


## Our Turn {.our-turn}

Let's add a dedicated page for the problem sets.

1. Make a new `ps-home.qmd`.
2. Link in navigation.
3. Add a listing.


## Your Turn {.your-turn}

Let's add a dedicated page for the problem sets.

1. Make a new `notes-home.qmd`.
2. Link in navigation.
3. Add a listing.


## Our Turn {.our-turn}

Let's made a dedicated staff website.

1. Change home page.
2. Add instructors page and link to it.
3. Add learning objectives to the notes.
